Multi-task learning in Computer Vision

### 2020-05-30 __latexindent_temp.tex
Add some fixes to all the things.

\chapter{Conclusions}
In this thesis, we have given an overview of fundamental computer vision tasks of image classification and object detection.
We described the importance of the ImageNet data set and some of the most significant image classification architectures based on it.
The importance of these models extend beyond just solving the ImageNet dataset, and we covered how it is possible to apply the trained models in new classification problems with transfer learning.

For object detection, we described how the problem and datasets differ from image classification ones.
We also described the different parts of object detectors and how single and two-stage detectors differ from one another and when one might be preferred over the other.
The object detectors also show how important the ImageNet backbones are, as they are an integral part of the object detection architectures also.
The focal loss is an important loss function used by modern single-stage object detectors in allowing a large number of anchor points for localizing the objects in the images.
Finally, we described one of the current state-of-the-art object detection architectures, the EfficientDet, and how it can be trained on a new problem using transfer learning like in the case of image classification.

Here we have also presented multi-task learning as a generalization of transfer learning.
In a multi-task setting, the goal is to solve multiple tasks using some shared representation. 
It differs from transfer learning in that all tasks are optimized continuously, rather than just serving as a starting point.
Doing transfer learning is an excellent way of obtaining good results, even on little data.
With multi-task training, we can utilize the common model architectures as shared parameters for multiple tasks to allow the model to generalize better and run more efficiently.
This is possible because the model is required to use the same capacity to solve multiple problems that may require different features, some of which can also be useful in other tasks. 
Still, sometimes the multi-task setting can be detrimental to accuracy.
Despite the differences in performance, utilizing shared representations means that there are fewer parameters that the model needs to learn, leading to smaller models and shorter inference times.

We saw multiple examples where multi-task learning played an important part in getting models that are efficient and performant.
One of these was the object detection, where the model tries to classify and localize the objects.
Both soft and hard parameter sharing for multi-task learning were covered, with some specialized architectures taking advantage of the fact that multiple tasks are solved at the same time.
Finally, we found that multiple tasks can serve as auxiliary targets for training to aid the model in finding important features.

A multi-task problem setting modifies the training process and introduces some new parameters that can be tuned when training models.
Task-specific sampling ratio during the data sampling process and giving task-specific loss weights were the two new factors that need to be tuned when different tasks are combined.
These weights need to be tuned appropriately for the model to be able to find the features that work for all tasks.
Beyond just tuning parameters, multi-task models may need some architectural fine-tuning in deciding which tasks should have shared representations and just how much should be shared.

The training process differences due to the multi-task problem setting were evaluated through multiple experiments on combining various datasets into a single model.
With these experiments, we empirically verified some of the assumptions of training the models in a multi-task setting.
We noted that it was difficult to find the very best models as different sampling ratios resulted in very different final models.
As the model gets larger and the number of tasks increases, finding the correct ratios gets ever more difficult.
After adding new tasks, the previous ratios might also need adjusting.
Also, we discussed the difficulties of modifying the existing models to contain our desired output heads.
This was most apparent in the case of object detectors. 
The supplied code is relatively pre-packaged to run on the specified training loop, and modifying these model definitions to add new tasks takes some effort.
We saw some improvements and reductions in the model performance, but in general, the multi-task models were close to the single-task counterparts so that reducing the model size might be a good trade-off.

In the end, what we learned is that the success of multi-task learning some tasks can't be pre-determined currently, and some expensive experimentation is needed to arrive at the best multi-task architecture.  
Thus, multi-task learning can be considered as a trade-off of training time complexity for inference-time benefits in accuracy and speed.

>>>>

@article{alexNet,
	title = {{ImageNet} classification with deep convolutional neural networks},
	volume = {60},
	issn = {00010782},
	url = {http://dl.acm.org/citation.cfm?doid=3098997.3065386},
	doi = {10.1145/3065386},
	abstract = {We trained a large, deep convolutional neural network to classify the 1.2 million high-resolution images in the ImageNet LSVRC-2010 contest into the 1000 different classes. On the test data, we achieved top-1 and top-5 error rates of 37.5\% and 17.0\% which is considerably better than the previous state-of-the-art. The neural network, which has 60 million parameters and 650,000 neurons, consists of ﬁve convolutional layers, some of which are followed by max-pooling layers, and three fully-connected layers with a ﬁnal 1000-way softmax. To make training faster, we used non-saturating neurons and a very efﬁcient GPU implementation of the convolution operation. To reduce overﬁtting in the fully-connected layers we employed a recently-developed regularization method called “dropout” that proved to be very effective. We also entered a variant of this model in the ILSVRC-2012 competition and achieved a winning top-5 test error rate of 15.3\%, compared to 26.2\% achieved by the second-best entry.},
	language = {en},
	number = {6},
	journal = {Communications of the ACM},
	author = {Krizhevsky, Alex and Sutskever, Ilya and Hinton, Geoffrey E.},
	year = {2017},
	pages = {84--90},
	file = {Krizhevsky et al. - 2017 - ImageNet classification with deep convolutional ne.pdf:/home/konstaku/Zotero/storage/45HSR2RH/Krizhevsky et al. - 2017 - ImageNet classification with deep convolutional ne.pdf:application/pdf}
}

@inproceedings{imagenet,
  title={Imagenet: A large-scale hierarchical image database},
  author={Deng, Jia and Dong, Wei and Socher, Richard and Li, Li-Jia and Li, Kai and Fei-Fei, Li},
  booktitle={2009 IEEE conference on computer vision and pattern recognition},
  pages={248--255},
  year={2009},
  organization={Ieee}
}

@misc{ILSVRC,
	title = {{ImageNet} {Large} {Scale} {Visual} {Recognition} {Competition} ({ILSVRC})},
	url = {http://www.image-net.org/challenges/LSVRC/},
	urldate = {2020-01-26},
	file = {ImageNet Large Scale Visual Recognition Competition (ILSVRC):/home/konstaku/Zotero/storage/2IGV2WF3/LSVRC.html:text/html}
}

@inproceedings{resNet,
  title={Deep residual learning for image recognition},
  author={He, Kaiming and Zhang, Xiangyu and Ren, Shaoqing and Sun, Jian},
  booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
  pages={770--778},
  year={2016}
}

@article{imageNet_summary,
  title={Imagenet large scale visual recognition challenge},
  author={Russakovsky, Olga and Deng, Jia and Su, Hao and Krause, Jonathan and Satheesh, Sanjeev and Ma, Sean and Huang, Zhiheng and Karpathy, Andrej and Khosla, Aditya and Bernstein, Michael and others},
  journal={International journal of computer vision},
  volume={115},
  number={3},
  pages={211--252},
  year={2015},
  publisher={Springer}
}

@inproceedings{objectNet,
  title={ObjectNet: A large-scale bias-controlled dataset for pushing the limits of object recognition models},
  author={Barbu, Andrei and Mayo, David and Alverio, Julian and Luo, William and Wang, Christopher and Gutfreund, Dan and Tenenbaum, Josh and Katz, Boris},
  booktitle={Advances in Neural Information Processing Systems},
  pages={9448--9458},
  year={2019}
}

@InProceedings{efficientNet,
  title = 	 {EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks},
  author = 	 {Tan, Mingxing and Le, Quoc},
  booktitle = 	 {Proceedings of the 36th International Conference on Machine Learning},
  pages = 	 {6105--6114},
  year = 	 {2019},
  editor = 	 {Chaudhuri, Kamalika and Salakhutdinov, Ruslan},
  volume = 	 {97},
  series = 	 {Proceedings of Machine Learning Research},
  address = 	 {Long Beach, California, USA},
  publisher = 	 {PMLR}
}

@inproceedings{betterTransfer,
  title={Do better imagenet models transfer better?},
  author={Kornblith, Simon and Shlens, Jonathon and Le, Quoc V},
  booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
  pages={2661--2671},
  year={2019}
}

@article{classifierPerformance,
title = {Compounding the {Performance} {Improvements} of {Assembled} {Techniques} in a {Convolutional} {Neural} {Network}},
url = {http://arxiv.org/abs/2001.06268},
abstract = {Recent studies in image classiﬁcation have demonstrated a variety of techniques for improving the performance of Convolutional Neural Networks (CNNs). However, attempts to combine existing techniques to create a practical model are still uncommon. In this study, we carry out extensive experiments to validate that carefully assembling these techniques and applying them to a basic CNN model in combination can improve the accuracy and robustness of the model while minimizing the loss of throughput. For example, our proposed ResNet-50 shows an improvement in top-1 accuracy from 76.3\% to 82.78\%, and an mCE improvement from 76.0\% to 48.9\%, on the ImageNet ILSVRC2012 validation set. With these improvements, inference throughput only decreases from 536 to 312. The resulting model signiﬁcantly outperforms state-of-theart models with similar accuracy in terms of mCE and inference throughput. To verify the performance improvement in transfer learning, ﬁne grained classiﬁcation and image retrieval tasks were tested on several open datasets and showed that the improvement to backbone network performance boosted transfer learning performance signiﬁcantly. Our approach achieved 1st place in the iFood Competition Fine-Grained Visual Recognition at CVPR 2019 1, and the source code and trained models will be made publicly available 2.},
language = {en},
journal = {arXiv:2001.06268 [cs]},
author = {Lee, Jungkyu and Won, Taeryun and Hong, Kiho},
year = {2020},
note = {arXiv: 2001.06268},
keywords = {Computer Science - Computer Vision and Pattern Recognition},
file = {Lee et al. - 2020 - Compounding the Performance Improvements of Assemb.pdf:/home/konstaku/Zotero/storage/788PI52C/Lee et al. - 2020 - Compounding the Performance Improvements of Assemb.pdf:application/pdf}
}

@article{leNet,
  title={Gradient-based learning applied to document recognition},
  author={LeCun, Yann and Bottou, L{\'e}on and Bengio, Yoshua and Haffner, Patrick},
  journal={Proceedings of the IEEE},
  volume={86},
  number={11},
  pages={2278--2324},
  year={1998},
  publisher={Ieee}
}

@inproceedings{rethinkTransfer,
  title={Rethinking imagenet pre-training},
  author={He, Kaiming and Girshick, Ross and Doll{\'a}r, Piotr},
  booktitle={Proceedings of the IEEE International Conference on Computer Vision},
  pages={4918--4927},
  year={2019}
}

@inproceedings{transferSurvey,
title = {A {Survey} of {Transfer} {Learning} for {Convolutional} {Neural} {Networks}},
doi = {10.1109/SIBGRAPI-T.2019.00010},
abstract = {Transfer learning is an emerging topic that may drive the success of machine learning in research and industry. The lack of data on specific tasks is one of the main reasons to use it, since collecting and labeling data can be very expensive and can take time, and recent concerns with privacy make difficult to use real data from users. The use of transfer learning helps to fast prototype new machine learning models using pre-trained models from a source task since training on millions of images can take time and requires expensive GPUs. In this survey, we review the concepts and definitions related to transfer learning and we list the different terms used in the literature. We bring the point of view from different authors of prior surveys, adding some more recent findings in order to give a clear vision of directions for future work in this field of research.},
booktitle = {2019 32nd {SIBGRAPI} {Conference} on {Graphics}, {Patterns} and {Images} {Tutorials} ({SIBGRAPI}-{T})},
author = {Ribani, Ricardo and Marengoni, Mauricio},
month = oct,
year = {2019},
note = {ISSN: 2474-0691},
keywords = {Machine learning, Convolutional Neural Networks, Data models, Deep Learning, Probability distribution, Supervised learning, Task analysis, Training, Transfer Learning},
pages = {47--57},
file = {IEEE Xplore Abstract Record:/home/konstaku/Zotero/storage/ZCESIJS9/8920338.html:text/html;IEEE Xplore Full Text PDF:/home/konstaku/Zotero/storage/PZN27DVW/Ribani and Marengoni - 2019 - A Survey of Transfer Learning for Convolutional Ne.pdf:application/pdf}
}

@article{transferSurvey2010,
	title = {A {Survey} on {Transfer} {Learning}},
	volume = {22},
	issn = {1041-4347},
	url = {http://ieeexplore.ieee.org/document/5288526/},
	doi = {10.1109/TKDE.2009.191},
	abstract = {A major assumption in many machine learning and data mining algorithms is that the training and future data must be in the same feature space and have the same distribution. However, in many real-world applications, this assumption may not hold. For example, we sometimes have a classiﬁcation task in one domain of interest, but we only have sufﬁcient training data in another domain of interest, where the latter data may be in a different feature space or follow a different data distribution. In such cases, knowledge transfer, if done successfully, would greatly improve the performance of learning by avoiding much expensive data labeling efforts. In recent years, transfer learning has emerged as a new learning framework to address this problem. This survey focuses on categorizing and reviewing the current progress on transfer learning for classiﬁcation, regression and clustering problems. In this survey, we discuss the relationship between transfer learning and other related machine learning techniques such as domain adaptation, multitask learning and sample selection bias, as well as co-variate shift. We also explore some potential future issues in transfer learning research.},
	language = {en},
	number = {10},
	journal = {IEEE Transactions on Knowledge and Data Engineering},
	author = {Pan, Sinno Jialin and Yang, Qiang},
	year = {2010},
	pages = {1345--1359},
	file = {Pan and Yang - 2010 - A Survey on Transfer Learning.pdf:/home/konstaku/Zotero/storage/YZBBSKDB/Pan and Yang - 2010 - A Survey on Transfer Learning.pdf:application/pdf}
}

@inproceedings{denseNet,
  title={Densely connected convolutional networks},
  author={Huang, Gao and Liu, Zhuang and Van Der Maaten, Laurens and Weinberger, Kilian Q},
  booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
  pages={4700--4708},
  year={2017}
}

@inproceedings{resNext,
  title={Aggregated residual transformations for deep neural networks},
  author={Xie, Saining and Girshick, Ross and Doll{\'a}r, Piotr and Tu, Zhuowen and He, Kaiming},
  booktitle={Proceedings of the IEEE conference on computer vision and pattern recognition},
  pages={1492--1500},
  year={2017}
}

@INPROCEEDINGS{mobileNetv2,

  author={M. {Sandler} and A. {Howard} and M. {Zhu} and A. {Zhmoginov} and L. {Chen}},

  booktitle={2018 IEEE/CVF Conference on Computer Vision and Pattern Recognition},

  title={MobileNetV2: Inverted Residuals and Linear Bottlenecks},

  year={2018},

  volume={},

  number={},

  pages={4510-4520},}

@incollection{gPipe,
title = {GPipe: Efficient Training of Giant Neural Networks using Pipeline Parallelism},
author = {Huang, Yanping and Cheng, Youlong and Bapna, Ankur and Firat, Orhan and Chen, Dehao and Chen, Mia and Lee, HyoukJoong and Ngiam, Jiquan and Le, Quoc V and Wu, Yonghui and Chen, zhifeng},
booktitle = {Advances in Neural Information Processing Systems 32},
editor = {H. Wallach and H. Larochelle and A. Beygelzimer and F. d\textquotesingle Alch\'{e}-Buc and E. Fox and R. Garnett},
pages = {103--112},
year = {2019},
publisher = {Curran Associates, Inc.},
url = {http://papers.nips.cc/paper/8305-gpipe-efficient-training-of-giant-neural-networks-using-pipeline-parallelism.pdf}
}

@article{mobileNet,
title = {{MobileNets}: {Efficient} {Convolutional} {Neural} {Networks} for {Mobile} {Vision} {Applications}},
shorttitle = {{MobileNets}},
url = {http://arxiv.org/abs/1704.04861},
abstract = {We present a class of efﬁcient models called MobileNets for mobile and embedded vision applications. MobileNets are based on a streamlined architecture that uses depthwise separable convolutions to build light weight deep neural networks. We introduce two simple global hyperparameters that efﬁciently trade off between latency and accuracy. These hyper-parameters allow the model builder to choose the right sized model for their application based on the constraints of the problem. We present extensive experiments on resource and accuracy tradeoffs and show strong performance compared to other popular models on ImageNet classiﬁcation. We then demonstrate the effectiveness of MobileNets across a wide range of applications and use cases including object detection, ﬁnegrain classiﬁcation, face attributes and large scale geo-localization.},
language = {en},
journal = {arXiv:1704.04861 [cs]},
author = {Howard, Andrew G. and Zhu, Menglong and Chen, Bo and Kalenichenko, Dmitry and Wang, Weijun and Weyand, Tobias and Andreetto, Marco and Adam, Hartwig},
year = {2017},
note = {arXiv: 1704.04861},
keywords = {Computer Science - Computer Vision and Pattern Recognition},
file = {Howard et al. - 2017 - MobileNets Efficient Convolutional Neural Network.pdf:/home/konstaku/Zotero/storage/DGE2QG6B/Howard et al. - 2017 - MobileNets Efficient Convolutional Neural Network.pdf:application/pdf}
}

        @inproceedings{wideResNet,
        	title={Wide Residual Networks},
        	author={Sergey Zagoruyko and Nikos Komodakis},
        	year={2016},
        	pages={87.1-87.12},
        	articleno={87},
        	numpages={12},
        	booktitle={Proceedings of the British Machine Vision Conference (BMVC)},
        	publisher={BMVA Press},
        	editor={Richard C. Wilson, Edwin R. Hancock and William A. P. Smith},
        	doi={10.5244/C.30.87},
        	isbn={1-901725-59-6},
        	url={https://dx.doi.org/10.5244/C.30.87}
        }
@INPROCEEDINGS{mnas,

  author={M. {Tan} and B. {Chen} and R. {Pang} and V. {Vasudevan} and M. {Sandler} and A. {Howard} and Q. V. {Le}},

  booktitle={2019 IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)},

  title={MnasNet: Platform-Aware Neural Architecture Search for Mobile},

  year={2019},

  volume={},

  number={},

  pages={2815-2823},}

@incollection{neuralSearch,
	location = {Cham},
	title = {Neural Architecture Search},
	isbn = {978-3-030-05318-5},
	url = {https://doi.org/10.1007/978-3-030-05318-5_3},
	series = {The Springer Series on Challenges in Machine Learning},
	abstract = {Deep Learning has enabled remarkable progress over the last years on a variety of tasks, such as image recognition, speech recognition, and machine translation. One crucial aspect for this progress are novel neural architectures. Currently employed architectures have mostly been developed manually by human experts, which is a time-consuming and error-prone process. Because of this, there is growing interest in automated neural architecture search methods. We provide an overview of existing work in this field of research and categorize them according to three dimensions: search space, search strategy, and performance estimation strategy.},
	pages = {63--77},
	booktitle = {Automated Machine Learning: Methods, Systems, Challenges},
	publisher = {Springer International Publishing},
	author = {Elsken, Thomas and Metzen, Jan Hendrik and Hutter, Frank},
	editor = {Hutter, Frank and Kotthoff, Lars and Vanschoren, Joaquin},
	date = {2019},
	langid = {english},
	doi = {10.1007/978-3-030-05318-5_3},
	file = {Springer Full Text PDF:/Users/kokutvon/Zotero/storage/JXSPZ6W9/Elsken et al. - 2019 - Neural Architecture Search.pdf:application/pdf}
}

@incollection{mutualLearning,
address = {Cham},
title = {Mutual {Learning} to {Adapt} for {Joint} {Human} {Parsing} and {Pose} {Estimation}},
volume = {11209},
isbn = {978-3-030-01227-4 978-3-030-01228-1},
url = {http://link.springer.com/10.1007/978-3-030-01228-1_31},
abstract = {This paper presents a novel Mutual Learning to Adapt model (MuLA) for joint human parsing and pose estimation. It eﬀectively exploits mutual beneﬁts from both tasks and simultaneously boosts their performance. Diﬀerent from existing post-processing or multi-task learning based methods, MuLA predicts dynamic task-speciﬁc model parameters via recurrently leveraging guidance information from its parallel tasks. Thus MuLA can fast adapt parsing and pose models to provide more powerful representations by incorporating information from their counterparts, giving more robust and accurate results. MuLA is implemented with convolutional neural networks and end-to-end trainable. Comprehensive experiments on benchmarks LIP and extended PASCALPerson-Part demonstrate the eﬀectiveness of the proposed MuLA model with superior performance to well established baselines.},
language = {en},
urldate = {2020-02-26},
booktitle = {Computer {Vision} – {ECCV} 2018},
publisher = {Springer International Publishing},
author = {Nie, Xuecheng and Feng, Jiashi and Yan, Shuicheng},
editor = {Ferrari, Vittorio and Hebert, Martial and Sminchisescu, Cristian and Weiss, Yair},
year = {2018},
doi = {10.1007/978-3-030-01228-1_31},
pages = {519--534},
file = {Nie et al. - 2018 - Mutual Learning to Adapt for Joint Human Parsing a.pdf:/home/konstaku/Zotero/storage/8QYIV5FG/Nie et al. - 2018 - Mutual Learning to Adapt for Joint Human Parsing a.pdf:application/pdf}
}

@inproceedings{multiLearningUncertainty,
address = {Salt Lake City, UT, USA},
title = {Multi-task {Learning} {Using} {Uncertainty} to {Weigh} {Losses} for {Scene} {Geometry} and {Semantics}},
isbn = {978-1-5386-6420-9},
url = {https://ieeexplore.ieee.org/document/8578879/},
doi = {10.1109/CVPR.2018.00781},
abstract = {Numerous deep learning applications beneﬁt from multitask learning with multiple regression and classiﬁcation objectives. In this paper we make the observation that the performance of such systems is strongly dependent on the relative weighting between each task’s loss. Tuning these weights by hand is a difﬁcult and expensive process, making multi-task learning prohibitive in practice. We propose a principled approach to multi-task deep learning which weighs multiple loss functions by considering the homoscedastic uncertainty of each task. This allows us to simultaneously learn various quantities with different units or scales in both classiﬁcation and regression settings. We demonstrate our model learning per-pixel depth regression, semantic and instance segmentation from a monocular input image. Perhaps surprisingly, we show our model can learn multi-task weightings and outperform separate models trained individually on each task.},
language = {en},
urldate = {2020-01-15},
booktitle = {2018 {IEEE}/{CVF} {Conference} on {Computer} {Vision} and {Pattern} {Recognition}},
publisher = {IEEE},
author = {Cipolla, Roberto and Gal, Yarin and Kendall, Alex},
year = {2018},
pages = {7482--7491},
file = {Cipolla et al. - 2018 - Multi-task Learning Using Uncertainty to Weigh Los.pdf:/home/konstaku/Zotero/storage/JUFEPU8D/Cipolla et al. - 2018 - Multi-task Learning Using Uncertainty to Weigh Los.pdf:application/pdf}
}

@inproceedings{visualPerson,
  title = {Visual Person Understanding Through Multi-task and Multi-dataset Learning},
  author = {Kilian Pfeiffer and Alexander Hermans and Istv\'{a}n S\'{a}r\'{a}ndi and Mark Weber and Bastian Leibe},
  booktitle = {German Conference on Pattern Recognition},
  pages = {551--566},
  date = {2019},
}

@article{multiDepth,
title = {{MultiDepth}: {Single}-{Image} {Depth} {Estimation} via {Multi}-{Task} {Regression} and {Classification}},
shorttitle = {{MultiDepth}},
url = {http://arxiv.org/abs/1907.11111},
abstract = {We introduce MultiDepth, a novel training strategy and convolutional neural network (CNN) architecture that allows approaching single-image depth estimation (SIDE) as a multi-task problem. SIDE is an important part of road scene understanding. It, thus, plays a vital role in advanced driver assistance systems and autonomous vehicles. Best results for the SIDE task so far have been achieved using deep CNNs. However, optimization of regression problems, such as estimating depth, is still a challenging task. For the related tasks of image classification and semantic segmentation, numerous CNN-based methods with robust training behavior have been proposed. Hence, in order to overcome the notorious instability and slow convergence of depth value regression during training, MultiDepth makes use of depth interval classification as an auxiliary task. The auxiliary task can be disabled at test-time to predict continuous depth values using the main regression branch more efficiently. We applied MultiDepth to road scenes and present results on the KITTI depth prediction dataset. In experiments, we were able to show that end-to-end multi-task learning with both, regression and classification, is able to considerably improve training and yield more accurate results.},
language = {en},
urldate = {2020-01-29},
journal = {arXiv:1907.11111 [cs]},
author = {Liebel, Lukas and Körner, Marco},
month = jul,
year = {2019},
note = {arXiv: 1907.11111},
keywords = {Computer Science - Computer Vision and Pattern Recognition},
file = {Liebel and Körner - 2019 - MultiDepth Single-Image Depth Estimation via Mult.pdf:/home/konstaku/Zotero/storage/PWEGEBIU/Liebel and Körner - 2019 - MultiDepth Single-Image Depth Estimation via Mult.pdf:application/pdf}
}

@inproceedings{taskonomy,
  title={Taskonomy: Disentangling task transfer learning},
  author={Zamir, Amir R and Sax, Alexander and Shen, William and Guibas, Leonidas J and Malik, Jitendra and Savarese, Silvio},
  booktitle={Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition},
  pages={3712--3722},
  year={2018}
}

@inproceedings{multiTaskAttention,
address = {Long Beach, CA, USA},
title = {End-{To}-{End} {Multi}-{Task} {Learning} {With} {Attention}},
isbn = {978-1-72813-293-8},
url = {https://ieeexplore.ieee.org/document/8954221/},
doi = {10.1109/CVPR.2019.00197},
abstract = {We propose a novel multi-task learning architecture, which allows learning of task-speciﬁc feature-level attention. Our design, the Multi-Task Attention Network (MTAN), consists of a single shared network containing a global feature pool, together with a soft-attention module for each task. These modules allow for learning of taskspeciﬁc features from the global features, whilst simultaneously allowing for features to be shared across different tasks. The architecture can be trained end-to-end and can be built upon any feed-forward neural network, is simple to implement, and is parameter efﬁcient. We evaluate our approach on a variety of datasets, across both image-toimage predictions and image classiﬁcation tasks. We show that our architecture is state-of-the-art in multi-task learning compared to existing methods, and is also less sensitive to various weighting schemes in the multi-task loss function. Code is available at https://github.com/ lorenmt/mtan.},
language = {en},
booktitle = {2019 {IEEE}/{CVF} {Conference} on {Computer} {Vision} and {Pattern} {Recognition} ({CVPR})},
publisher = {IEEE},
author = {Liu, Shikun and Johns, Edward and Davison, Andrew J.},
year = {2019},
pages = {1871--1880},
file = {Liu et al. - 2019 - End-To-End Multi-Task Learning With Attention.pdf:/home/konstaku/Zotero/storage/6Z9IWAEJ/Liu et al. - 2019 - End-To-End Multi-Task Learning With Attention.pdf:application/pdf}
}
@inproceedings{crossStitch,

  author={I. {Misra} and A. {Shrivastava} and A. {Gupta} and M. {Hebert}},

  booktitle={2016 IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},

  title={Cross-Stitch Networks for Multi-task Learning},

  year={2016},

  volume={},

  number={},

  pages={3994-4003},}

@article{learningToMultitask,
	title = {Learning to {Multitask}},
	abstract = {Multitask learning has shown promising performance in many applications and many multitask models have been proposed. In order to identify an effective multitask model for a given multitask problem, we propose a learning framework called Learning to MultiTask (L2MT). To achieve the goal, L2MT exploits historical multitask experience which is organized as a training set consisting of several tuples, each of which contains a multitask problem with multiple tasks, a multitask model, and the relative test error. Based on such training set, L2MT ﬁrst uses a proposed layerwise graph neural network to learn task embeddings for all the tasks in a multitask problem and then learns an estimation function to estimate the relative test error based on task embeddings and the representation of the multitask model based on a uniﬁed formulation. Given a new multitask problem, the estimation function is used to identify a suitable multitask model. Experiments on benchmark datasets show the effectiveness of the proposed L2MT framework.},
	language = {en},
	author = {Zhang, Yu and Wei, Ying and Yang, Qiang},
	pages = {12},
	file = {Zhang et al. - Learning to Multitask.pdf:/home/konstaku/Zotero/storage/CSZ75VG5/Zhang et al. - Learning to Multitask.pdf:application/pdf}
}

@inproceedings{usingUncertaintyToWeighLosses,
address = {Salt Lake City, UT, USA},
title = {Multi-task {Learning} {Using} {Uncertainty} to {Weigh} {Losses} for {Scene} {Geometry} and {Semantics}},
isbn = {978-1-5386-6420-9},
url = {https://ieeexplore.ieee.org/document/8578879/},
doi = {10.1109/CVPR.2018.00781},
abstract = {Numerous deep learning applications beneﬁt from multitask learning with multiple regression and classiﬁcation objectives. In this paper we make the observation that the performance of such systems is strongly dependent on the relative weighting between each task’s loss. Tuning these weights by hand is a difﬁcult and expensive process, making multi-task learning prohibitive in practice. We propose a principled approach to multi-task deep learning which weighs multiple loss functions by considering the homoscedastic uncertainty of each task. This allows us to simultaneously learn various quantities with different units or scales in both classiﬁcation and regression settings. We demonstrate our model learning per-pixel depth regression, semantic and instance segmentation from a monocular input image. Perhaps surprisingly, we show our model can learn multi-task weightings and outperform separate models trained individually on each task.},
language = {en},
booktitle = {2018 {IEEE}/{CVF} {Conference} on {Computer} {Vision} and {Pattern} {Recognition}},
publisher = {IEEE},
author = {Cipolla, Roberto and Gal, Yarin and Kendall, Alex},
month = jun,
year = {2018},
pages = {7482--7491},
file = {Cipolla et al. - 2018 - Multi-task Learning Using Uncertainty to Weigh Los.pdf:/home/konstaku/Zotero/storage/JUFEPU8D/Cipolla et al. - 2018 - Multi-task Learning Using Uncertainty to Weigh Los.pdf:application/pdf}
}

@article{lossWeighting,
	title = {A {Comparison} of {Loss} {Weighting} {Strategies} for {Multi} task {Learning} in {Deep} {Neural} {Networks}},
	volume = {7},
	issn = {2169-3536},
	doi = {10.1109/ACCESS.2019.2943604},
	abstract = {With the success of deep learning in a wide variety of areas, many deep multi-task learning (MTL) models have been proposed claiming improvements in performance obtained by sharing the learned structure across several related tasks. However, the dynamics of multi-task learning in deep neural networks is still not well understood at either the theoretical or experimental level. In particular, the usefulness of different task pairs is not known a priori. Practically, this means that properly combining the losses of different tasks becomes a critical issue in multi-task learning, as different methods may yield different results. In this paper, we benchmarked different multi-task learning approaches using shared trunk with task specific branches architecture across three different MTL datasets. For the first dataset, i.e. Multi-MNIST (Modified National Institute of Standards and Technology database), we thoroughly tested several weighting strategies, including simply adding task-specific cost functions together, dynamic weight average (DWA) and uncertainty weighting methods each with various amounts of training data per-task. We find that multi-task learning typically does not improve performance for a user-defined combination of tasks. Further experiments evaluated on diverse tasks and network architectures on various datasets suggested that multi-task learning requires careful selection of both task pairs and weighting strategies to equal or exceed the performance of single task learning.},
	journal = {IEEE Access},
	author = {Gong, Ting and Lee, Tyler and Stephenson, Cory and Renduchintala, Venkata and Padhy, Suchismita and Ndirango, Anthony and Keskin, Gokce and Elibol, Oguz H.},
	year = {2019},
	keywords = {Data models, Task analysis, Training, Deep learning, deep multitask learning models, deep neural networks, dynamic weight average, Dynamic weighting average, Estimation, learning (artificial intelligence), loss weighting strategies, multi-MNIST, multi-objective optimization, multi-task learning, neural nets, task pairs, task specific branches architecture, task-specific cost functions, Training data, Uncertainty, uncertainty weighting},
	pages = {141627--141632},
	file = {IEEE Xplore Abstract Record:/home/konstaku/Zotero/storage/XGGZ8FTG/8848395.html:text/html;IEEE Xplore Full Text PDF:/home/konstaku/Zotero/storage/R9J46AED/Gong et al. - 2019 - A Comparison of Loss Weighting Strategies for Mult.pdf:application/pdf}
}

@article{surveyOnMultiTask,
title = {A {Survey} on {Multi}-{Task} {Learning}},
url = {http://arxiv.org/abs/1707.08114},
abstract = {Multi-Task Learning (MTL) is a learning paradigm in machine learning and its aim is to leverage useful information contained in multiple related tasks to help improve the generalization performance of all the tasks. In this paper, we give a survey for MTL. First, we classify different MTL algorithms into several categories, including feature learning approach, low-rank approach, task clustering approach, task relation learning approach, and decomposition approach, and then discuss the characteristics of each approach. In order to improve the performance of learning tasks further, MTL can be combined with other learning paradigms including semi-supervised learning, active learning, unsupervised learning, reinforcement learning, multi-view learning and graphical models. When the number of tasks is large or the data dimensionality is high, batch MTL models are difﬁcult to handle this situation and online, parallel and distributed MTL models as well as dimensionality reduction and feature hashing are reviewed to reveal their computational and storage advantages. Many real-world applications use MTL to boost their performance and we review representative works.},
language = {en},
journal = {arXiv:1707.08114 [cs]},
author = {Zhang, Yu and Yang, Qiang},
year = {2018},
note = {arXiv: 1707.08114},
keywords = {Computer Science - Artificial Intelligence, Computer Science - Machine Learning},
file = {Zhang and Yang - 2018 - A Survey on Multi-Task Learning.pdf:/home/konstaku/Zotero/storage/ZZDVVBMV/Zhang and Yang - 2018 - A Survey on Multi-Task Learning.pdf:application/pdf}
}

@article{origMultitask,
	title = {Multitask {Learning}},
	abstract = {Multitask Learning is an approach to inductive transfer that improves generalization by using the domain information contained in the training signals of related tasks as an inductive bias. It does this by learning tasks in parallel while using a shared representation; what is learned for each task can help other tasks be learned better. This paper reviews prior work on MTL, presents new evidence that MTL in backprop nets discovers task relatedness without the need of supervisory signals, and presents new results for MTL with k-nearest neighbor and kernel regression. In this paper we demonstrate multitask learning in three domains. We explain how multitask learning works, and show that there are many opportunities for multitask learning in real domains. We present an algorithm and results for multitask learning with case-based methods like k-nearest neighbor and kernel regression, and sketch an algorithm for multitask learning in decision trees. Because multitask learning works, can be applied to many different kinds of domains, and can be used with different learning algorithms, we conjecture there will be many opportunities for its use on real-world problems.},
	language = {en},
	author = {Caruana, Rich},
	year= {1997},
	pages = {35},
	file = {Caruana - Multitask Learning.pdf:/home/konstaku/Zotero/storage/5IZMB2MK/Caruana - Multitask Learning.pdf:application/pdf}
}
